---
title: "MOT_Sequence_Creation"
author: "Freya Joessel"
editor: source
date: today
toc: true
toc-depth: 5
# toc-expand: true
number-sections: true
highlight-style: pygments
toc-location: left
reference-location: margin
citation-location: margin
format:
  html: 
    code-fold: true
    html-math-method: katex
---


```{r preamble}
#| echo: false
#| include: false

library(dplyr)
library(progress)
library(ggplot2)
library(purrr)
library(parallel)
library(gganimate)

```

```{r load-data}
#| echo: false
#| cache: true
#| include: false

if (file.exists("Tables/density_per_frame_tables_all.rds")) {
  density_per_frame_tables_all.df <- readRDS(file = "Tables/density_per_frame_tables_all.rds")
} else {
  density_table.df <- read.csv("Tables/density_table.csv", stringsAsFactors = FALSE)
  density_per_frame_table.df <- read.csv("Tables/density_per_frame_table.csv", stringsAsFactors = FALSE)
  
  density_per_frame_tables.list <- list(
    density_per_frame_table.df,
    read.csv("Tables/density_per_frame_table_5678.csv", stringsAsFactors = FALSE),
    read.csv("Tables/density_per_frame_table_2222.csv", stringsAsFactors = FALSE),
    read.csv("Tables/density_per_frame_table_8888.csv", stringsAsFactors = FALSE),
    read.csv("Tables/density_per_frame_table_3995.csv", stringsAsFactors = FALSE))
  
  density_per_frame_tables_2.list <- list(
    read.csv("Tables/density_per_frame_table_3143.csv", stringsAsFactors = FALSE),
    read.csv("Tables/density_per_frame_table_1618.csv", stringsAsFactors = FALSE),
    read.csv("Tables/density_per_frame_table_9876.csv", stringsAsFactors = FALSE),
    read.csv("Tables/density_per_frame_table_9999.csv", stringsAsFactors = FALSE))
  
  density_per_frame_tables_all.list <- 
    c(density_per_frame_tables.list, density_per_frame_tables_2.list)

  for (i_dataset in 1:length(density_per_frame_tables_all.list)) {
    density_per_frame_tables_all.list[[i_dataset]] <-
      density_per_frame_tables_all.list[[i_dataset]] %>% 
      mutate(i_dataset = i_dataset)
  }
  
  density_per_frame_tables_all.df <- bind_rows(density_per_frame_tables_all.list)
    
  saveRDS(object = density_per_frame_tables_all.df, file = "Tables/density_per_frame_tables_all.rds")
}

```

# Task Parameters

```{r task-parameters}
#| echo: false
#| include: false

n_targets_in_experiment <- 5

tracking_duration_s <- 4
trial_duration_s <- 6
probing_duration <- trial_duration_s - tracking_duration_s
trial_n_frames <- max(density_per_frame_tables_all.df$frame_num)
probing_n_frames <- probing_duration*(trial_n_frames - 1)/trial_duration_s + 1
tracking_n_frames <- trial_n_frames - probing_n_frames

```

We opt for N targets to track = `r n_targets_in_experiment` to have enough room above and below the typical performance of young adults at this variant of the MOT task (around 75% - Green and Bavelier (2006)). 

# Investigating Density Values

To define the threshold for low or high density throughout a trial, we compute the median of the density of dots collapsed across trials, frames, and circles. This gives us an empirical estimate of a threshold for the density where 50% of trajectory would be above this threshold and 50% would be above. 

```{r median-density}
#| echo: false
#| include: false

density_threshold <- list()
density_threshold$median <- median(density_per_frame_tables_all.df$density)
density_threshold$sd <- sd(density_per_frame_tables_all.df$density)
density_threshold$mean <- mean(density_per_frame_tables_all.df$density) 
# density_threshold$ci95 <- Hmisc::smean.cl.boot(density_per_frame_table.df$density) 

```

```{r median-density-plot}
#| echo: false
#| include: false

density_hist.plot <- ggplot() +
  geom_histogram(data = density_per_frame_tables_all.df, aes(x = density), bins = 50) + 
  geom_vline(aes(xintercept = density_threshold$median), colour = "red", linetype = "dashed") + 
  geom_vline(aes(xintercept = density_threshold$median - density_threshold$sd), colour = "red", linetype = "dotted") + 
  geom_vline(aes(xintercept = density_threshold$median + density_threshold$sd), colour = "red", linetype = "dotted")

```

```{r median-density-display}
#| echo: false
#| fig-cap: "Density Histogram"
#| cap-location: margin
#| out.width: "70%"
#| fig.align: "center"
#| cache: true

density_hist.plot
```

# Density Low/High Throughout

## Estimating the number of frames

For each existing trajectory, let's estimate for how many frames each dot has a density above the threshold and below the threshold *during the tracking period*. 


```{r n-frames-above-threshold-tracking-period}
#| echo: false
#| include: false
#| cache: true

n_frames_above_threshold.df <- density_per_frame_tables_all.df %>% 
  filter(frame_num > probing_n_frames) %>%
  group_by(trial_num, circle_num) %>% 
  dplyr::summarise(n_frames_above_threshold = sum(density > density_threshold$median)) %>%
  mutate(n_frames_above_threshold_perc = n_frames_above_threshold/max(density_per_frame_tables_all.df$frame_num))

n_frames_above_threshold_hist.plot <- ggplot() + 
  geom_histogram(data = n_frames_above_threshold.df, aes(x = n_frames_above_threshold_perc), bins = 50)

```

```{r n-frames-above-threshold-tracking-period-display}
#| echo: false
#| fig-cap: "Density Histogram"
#| cap-location: margin
#| out.width: "70%"
#| fig.align: "center"
#| cache: true

n_frames_above_threshold_hist.plot
```

Let's confirm that the spikes in the lowest and highest bins actually contains trajectories with all frames either above (1) or below (0) the threshold.

```{r trajectories-above-below-threshold-tracking-period}
#| echo: false
#| include: false

n_trajectories_full_above_or_below.df <- n_frames_above_threshold.df %>%
  ungroup() %>% 
  count(n_frames_above_threshold)

n_full_above <- n_trajectories_full_above_or_below.df %>% 
  filter(n_frames_above_threshold == tracking_n_frames) %>% 
  pull(n)

n_full_below <- n_trajectories_full_above_or_below.df %>% 
  filter(n_frames_above_threshold == 0) %>% 
  pull(n)

```

There are `r n_full_above` trajectories with a density above the threshold at all frames, and `r n_full_below` trajectories with a density below the threshold at all frames. So now we move on to investigating how many trajectories are always under/below the threshold for each trial. 

```{r count-trajectories-tracking-period}
#| echo: false
#| include: false
#| cache: true

n_frames_above_threshold_density.df <- density_per_frame_tables_all.df %>% 
  filter(frame_num > probing_n_frames) %>%
  group_by(i_dataset, trial_num, circle_num) %>% 
  dplyr::reframe(n_frames_above_threshold = sum(density > density_threshold$median),
                 n_frames_above_threshold_perc = n_frames_above_threshold/n())

write.csv(n_frames_above_threshold_density.df, file = "Tables/n_frames_above_threshold_density.csv", row.names = F)
saveRDS(n_frames_above_threshold_density.df, file = "Tables/n_frames_above_threshold_density.rds")


n_trajectories_full_above_or_below_per_trial.df <- n_frames_above_threshold.df %>%
  group_by(i_dataset, trial_num) %>% 
  reframe(n_full_above = sum(n_frames_above_threshold_perc == 1),
          n_full_below = sum(n_frames_above_threshold_perc == 0), 
          n_95_above = sum(n_frames_above_threshold_perc >= 0.95),
          n_95_below = sum(n_frames_above_threshold_perc <= 0.05), 
          n_90_above = sum(n_frames_above_threshold_perc >= 0.90),
          n_90_below = sum(n_frames_above_threshold_perc <= 0.10))

trials_to_keep_above.df <-  n_trajectories_full_above_or_below_per_trial.df %>% 
  filter(n_full_above == n_targets_in_experiment)
n_possible_trials_above <- nrow(trials_to_keep_above.df)

trials_to_keep_below.df <-  n_trajectories_full_above_or_below_per_trial.df %>% 
  filter(n_full_below == n_targets_in_experiment)
n_possible_trials_below <- nrow(trials_to_keep_below.df)

write.csv(trials_to_keep_above.df, file = "Tables/trials_to_keep-above_threshold_throughout.csv", row.names = F)
write.csv(trials_to_keep_below.df, file = "Tables/trials_to_keep-below_threshold_throughout.csv", row.names = F)

saveRDS(trials_to_keep_above.df, file = "Tables/trials_to_keep-above_threshold_throughout.rds")
saveRDS(trials_to_keep_below.df, file = "Tables/trials_to_keep-below_threshold_throughout.rds")


# Trials To Keep Above
trials_to_keep_above.str <- paste(trials_to_keep_above.df$i_dataset, 
                                  trials_to_keep_above.df$trial_num, 
                                  sep = "-")

density_per_frame_tables_above_throughout.df <- 
  density_per_frame_tables_all.df %>% 
  mutate(trial_id = paste(i_dataset, trial_num, sep = "-")) %>% 
  filter(trial_id %in% trials_to_keep_above.str)
  
# Trials To Keep Below
trials_to_keep_below.str <- paste(trials_to_keep_below.df$i_dataset, 
                                  trials_to_keep_below.df$trial_num, 
                                  sep = "-")

density_per_frame_tables_below_throughout.df <- 
  density_per_frame_tables_all.df %>% 
  mutate(trial_id = paste(i_dataset, trial_num, sep = "-")) %>% 
  filter(trial_id %in% trials_to_keep_below.str)

write.csv(density_per_frame_tables_above_throughout.df, file = "Tables/density_per_frame_tables_above_throughout.csv", row.names = F)
write.csv(density_per_frame_tables_below_throughout.df, file = "Tables/density_per_frame_tables_below_throughout.csv", row.names = F)

saveRDS(density_per_frame_tables_above_throughout.df, file = "Tables/density_per_frame_tables_above_throughout.rds")
saveRDS(density_per_frame_tables_below_throughout.df, file = "Tables/density_per_frame_tables_below_throughout.rds")



```

## Potential Trials

And here are the trials we can pick from for the "above" and "below" condition trials. There are `r n_possible_trials_above` possible trials for the above condition and `r n_possible_trials_below` for the below condition. 

```{r final-above-trials-tracking-period}
#| echo: false
#| tbl-cap: "Trials for the above condition"  
#| cap-location: top

knitr::kable(trials_to_keep_above.df)
```

```{r final-below-trials-tracking-period}
#| echo: false
#| tbl-cap: "Trials for the below condition"  
#| cap-location: top

knitr::kable(trials_to_keep_below.df)
```

# Low-to-High and High-to-Low Densities

We define out low-to-high trials as trials with a density above the threshold for the initial X seconds of the tracking period and below the threshold for the last X seconds of the tracking period, and vice versa for high-to-low trials. First, we need to understand what value for X makes sense.  

## Estimating the duration for the initial and final periods

```{r low-to-high-density}
#| echo: false
#| include: false
#| cache: true

beginning_period_start_time <- probing_duration
end_period_end_time <- trial_duration_s
frames_per_seconds <- (trial_n_frames - 1)/trial_duration_s

potential_frames.df <- 
  data.frame(potential_period_durations = seq(1, 1.7, 0.05)) %>% 
  mutate(beginning_period_start_frame = beginning_period_start_time*frames_per_seconds + 1,
         beginning_period_end_frame = (potential_period_durations + beginning_period_start_time)*frames_per_seconds + 1,
         end_period_start_frame = (trial_duration_s - potential_period_durations)*frames_per_seconds + 1,
         end_period_end_frame = trial_n_frames,
         potential_period_n_frames = beginning_period_end_frame - beginning_period_start_frame + 1)

fname_high_low_periods <- "Tables/high_low_periods.rds"
if (file.exists(fname_high_low_periods)) {
  high_low_periods.df <- readRDS(file = fname_high_low_periods)
} else {
  high_low_periods.list <- list()
  
  pb <- progress_bar$new(total = nrow(potential_frames.df))
  pb$tick(0)
    
  for (i_potential_duration in 1:nrow(potential_frames.df)) {
  # for (i_potential_duration in 1:3) {
  
    beg_period_strt_frm <- potential_frames.df$beginning_period_start_frame[i_potential_duration]
    beg_period_end_frm <- potential_frames.df$beginning_period_end_frame[i_potential_duration]
    end_period_strt_frm <- potential_frames.df$end_period_start_frame[i_potential_duration]
    end_period_end_frm <- potential_frames.df$end_period_end_frame[i_potential_duration]
    
    high_low_periods.list[[i_potential_duration]] <- 
      density_per_frame_tables_all.df %>% 
      mutate(beginning_end = ifelse(frame_num >= beg_period_strt_frm & 
                                      frame_num <= beg_period_end_frm, 
                                    "beginning", 
                                    ifelse(frame_num >= end_period_strt_frm & 
                                      frame_num <= end_period_end_frm, 
                                      "end", "none"))) %>% 
      filter(beginning_end != "none") %>% 
      group_by(i_dataset, trial_num, circle_num, beginning_end) %>% 
      reframe(period_n_frames_high = sum(density > density_threshold$median), 
              period_n_frames_low = sum(density < density_threshold$median), 
              period_n_frames_perc_high = period_n_frames_high/n(),
              period_n_frames_perc_low = period_n_frames_low/n()) %>% 
      mutate(potential_period_duration = 
               potential_frames.df$potential_period_durations[i_potential_duration], 
             potential_period_n_frames = 
               potential_frames.df$potential_period_n_frames[i_potential_duration])
    
    pb$tick()
  }
  
  high_low_periods.df <- bind_rows(high_low_periods.list)
  saveRDS(object = high_low_periods.df, file = fname_high_low_periods)
  write.csv(x = high_low_periods.df, file = gsub(".rds", ".csv", fname_high_low_periods))
}



```

```{r low-to-high-density-counts}
#| echo: false
#| include: false

high_low_periods_wide.df <- high_low_periods.df %>% 
  tidyr::pivot_wider(values_from = c(period_n_frames_high,
                                     period_n_frames_low, 
                                     period_n_frames_perc_high,
                                     period_n_frames_perc_low),
                     names_from = beginning_end, 
                     names_sep = "_") %>% 
  mutate(high_to_low_category = 
           ifelse(period_n_frames_perc_high_beginning == 1 &
                    period_n_frames_perc_low_end == 1, 
                  "high-to-low", 
                  ifelse(period_n_frames_perc_low_beginning == 1 &
                    period_n_frames_perc_high_end == 1, 
                    "low-to-high", "none")), 
         trial_id = paste(i_dataset, trial_num, sep = "-")) 
names(high_low_periods_wide.df) <- gsub("^period_", "", names(high_low_periods_wide.df))

count_high_low_trajectories_per_trial.df <- high_low_periods_wide.df %>% 
  group_by(i_dataset, potential_period_duration, trial_num) %>% 
  count(high_to_low_category, name = "n_trajectories")

count_trial_per_high_low_categories.df <- 
  count_high_low_trajectories_per_trial.df %>% 
  group_by(potential_period_duration, high_to_low_category, n_trajectories) %>% 
  count()

count_trial_per_high_low_categories_for_plot.df <-  
  count_trial_per_high_low_categories.df %>% 
  filter(high_to_low_category != "none") %>%
  # filter(n_trajectories %in% c(4,5)) %>% 
  mutate(n = ifelse(n > 50, 50, n), 
         n_trajectories = factor(n_trajectories, levels = n_trajectories)) 


```

```{r low-to-high-density-plot}
#| echo: false
#| include: false

count_trial_per_high_low_categories.plot <- ggplot() + 
  geom_line(data = count_trial_per_high_low_categories_for_plot.df, 
             aes(x = potential_period_duration, y = n, color = n_trajectories)) + 
  geom_point(data = count_trial_per_high_low_categories_for_plot.df, 
             aes(x = potential_period_duration, y = n)) + 
  facet_grid(high_to_low_category ~ .) + 
  geom_hline(yintercept = 10, color = "red", linetype = "dotted") + 
  geom_hline(yintercept = 5, color = "red", linetype = "solid")

count_trial_per_high_low_categories.plot
```

```{r low-to-high-density-plot-display}
#| echo: false
#| fig-cap: "Number of trials with a given number of trajetcories in the low-to-high and high-to-low categories for each period duration."
#| cap-location: margin
#| out.width: "70%"
#| fig.align: "center"

count_trial_per_high_low_categories.plot
```

## Potential Trials

```{r extract-trials-for-low-high-density}
#| echo: false
#| include: false

period_duration <- 1.4

trials_to_keep_for_low_to_high_density.df <- 
  count_high_low_trajectories_per_trial.df %>% 
  filter(n_trajectories >= n_targets_in_experiment) %>% 
  filter(potential_period_duration == period_duration) %>% 
  filter(high_to_low_category == "low-to-high") %>% 
  mutate(trial_id = paste(i_dataset, trial_num, sep = "-"))
n_possible_trials_low_to_high <- nrow(trials_to_keep_for_low_to_high_density.df)

trials_to_keep_for_high_to_low_density.df <- 
  count_high_low_trajectories_per_trial.df %>% 
  filter(n_trajectories >= n_targets_in_experiment) %>% 
  filter(potential_period_duration == period_duration) %>% 
  filter(high_to_low_category == "high-to-low") %>% 
  mutate(trial_id = paste(i_dataset, trial_num, sep = "-"))
n_possible_trials_high_to_low <- nrow(trials_to_keep_for_high_to_low_density.df)


circles_low_to_high_threshold_density.df <- 
  high_low_periods_wide.df %>% 
  filter(trial_id %in% unique(trials_to_keep_for_low_to_high_density.df$trial_id),
         high_to_low_category == "low-to-high", 
         potential_period_duration == period_duration) %>% 
  group_by(i_dataset, trial_num, trial_id, high_to_low_category) %>% 
  mutate(n_traj = n()) %>% 
  filter(n_traj >= 5) %>% 
  dplyr::summarise(target_set = paste(circle_num, collapse = "-"), .groups = "drop") %>% 
  mutate(density_traj_type = high_to_low_category)

circles_high_to_low_threshold_density.df <- 
  high_low_periods_wide.df %>% 
  filter(trial_id %in% unique(trials_to_keep_for_high_to_low_density.df$trial_id),
         high_to_low_category == "high-to-low", 
         potential_period_duration == period_duration) %>% 
  group_by(i_dataset, trial_num, trial_id, high_to_low_category) %>% 
  mutate(n_traj = n()) %>% 
  filter(n_traj >= 5) %>% 
  dplyr::summarise(target_set = paste(circle_num, collapse = "-"), .groups = "drop") %>% 
  mutate(density_traj_type = high_to_low_category)

circles_high_low_threshold_density.df <- 
  bind_rows(
    circles_low_to_high_threshold_density.df, 
    circles_high_to_low_threshold_density.df
  ) %>% 
  mutate(target_density_traj_type = "all")

saveRDS(object = circles_high_low_threshold_density.df, 
        file = "Tables/circles_high_low_threshold_density.rds")
write.csv(x = circles_high_low_threshold_density.df, 
          file = "Tables/circles_high_low_threshold_density.csv", 
          row.names = F)

# Trials To Keep Low-To-High and High-To-Low
trials_to_keep_low_high.str <- circles_high_low_threshold_density.df$trial_id

info_per_frame_low_to_high_and_high_to_low.df <- 
  density_per_frame_tables_all.df %>% 
  mutate(trial_id = paste(i_dataset, trial_num, sep = "-")) %>% 
  filter(trial_id %in% trials_to_keep_low_high.str) %>% 
  merge(circles_high_low_threshold_density.df)

write.csv(info_per_frame_low_to_high_and_high_to_low.df, 
          file = "Tables/info_per_frame_low_to_high_and_high_to_low.csv", 
          row.names = F)
saveRDS(info_per_frame_low_to_high_and_high_to_low.df, 
        file = "Tables/info_per_frame_low_to_high_and_high_to_low.rds")


```


It seems that the maximum period duration given that we want 5 trajectories per trial is `r period_duration` seconds (we may be able to go to higher values if we simulate more trials). 

And here are the trials we can pick from for the "low-to-high" and "high-to-low" condition trials. There are `r n_possible_trials_low_to_high` possible trials for the above condition and `r n_possible_trials_high_to_low` for the below condition.


```{r extract-trials-for-high-to-low-density-tbl}
#| echo: false
#| tbl-cap: "Trials with the right number of high-to-low trajectories"  
#| cap-location: top

knitr::kable(trials_to_keep_for_low_to_high_density.df, align = "c")
```

```{r extract-trials-for-low-to-high-density-tbl}
#| echo: false
#| tbl-cap: "Trials with the right number of low-to-high trajectories"  
#| cap-location: top

knitr::kable(trials_to_keep_for_high_to_low_density.df, align = "c")
```

# Videos of potential trials

```{r find-sets-of-targets-with-density-above-threshold}

density_per_frame_tables_above_throughout.df <- readRDS(file = "Tables/density_per_frame_tables_above_throughout.rds") 
trial_ids_above_density <- unique(density_per_frame_tables_above_throughout.df$trial_id)

density_per_frame_tables_below_throughout.df <- readRDS(file = "Tables/density_per_frame_tables_below_throughout.rds") 
trial_ids_below_density <- unique(density_per_frame_tables_below_throughout.df$trial_id)

n_frames_above_threshold_density.df <- readRDS(file = "Tables/n_frames_above_threshold_density.rds")

circles_with_frames_above_threshold_density.df <- 
  n_frames_above_threshold_density.df %>% 
  mutate(trial_id = sprintf("%i-%i", i_dataset, trial_num)) %>% 
  filter(trial_id %in% trial_ids_above_density, 
         n_frames_above_threshold == 240) %>% 
  group_by(i_dataset, trial_num, trial_id) %>% 
  mutate(n_traj = n()) %>% 
  filter(n_traj == 5) %>% 
  dplyr::summarise(target_set = paste(circle_num, collapse = "-"), .groups = "drop") %>% 
  mutate(density_traj_type = "above")

circles_with_frames_below_threshold_density.df <- 
  n_frames_above_threshold_density.df %>% 
  mutate(trial_id = sprintf("%i-%i", i_dataset, trial_num)) %>% 
  filter(trial_id %in% trial_ids_below_density, 
         n_frames_above_threshold == 0) %>% 
  group_by(i_dataset, trial_num, trial_id) %>% 
  mutate(n_traj = n()) %>% 
  filter(n_traj == 5) %>% 
  dplyr::summarise(target_set = paste(circle_num, collapse = "-"), .groups = "drop") %>% 
  mutate(density_traj_type = "below")

circles_with_all_tracking_frames_threshold_density.df <- bind_rows(
  circles_with_frames_above_threshold_density.df,
  circles_with_frames_below_threshold_density.df
) %>% 
  mutate(target_density_traj_type = "all")

saveRDS(object = circles_with_all_tracking_frames_threshold_density.df, 
        file = "Tables/circles_with_all_tracking_frames_threshold_density.rds")
write.csv(x = circles_with_all_tracking_frames_threshold_density.df, 
          file = "Tables/circles_with_all_tracking_frames_threshold_density.csv", 
          row.names = F)


info_per_frame_traj_above_throughout.df <- 
  density_per_frame_tables_above_throughout.df %>% 
  mutate(density_traj_type = "above")

info_per_frame_traj_below_throughout.df <- 
  density_per_frame_tables_below_throughout.df %>% 
  mutate(density_traj_type = "below")

info_per_frame_traj_density_throughout.df <- bind_rows(
  info_per_frame_traj_above_throughout.df,
  info_per_frame_traj_below_throughout.df
)

saveRDS(object = info_per_frame_traj_density_throughout.df, 
        file = "Tables/info_per_frame_traj_density_throughout.rds")
write.csv(x = info_per_frame_traj_density_throughout.df, 
          file = "Tables/info_per_frame_traj_density_throughout.csv", 
          row.names = F)


```

```{r save-video-function}
#| echo: false
#| include: false

# ─────────────────────────────────────────────
# 1. Single-trial video saving function
# ─────────────────────────────────────────────

save_video <- function(trial_curr.df, density_per_frame_tables_all.df, video_dir,
                       log_file = NULL) {
  
  # Helper to write a timestamped line to this worker's dedicated log file
  log_msg <- function(msg) {
    if (!is.null(log_file)) {
      cat(sprintf("%s | %s\n", format(Sys.time(), "%Y-%m-%d %H:%M:%S"), msg),
          file = log_file, append = TRUE)
    }
  }
  
  trial_label <- sprintf("trial_%s-%s_%s_%s",
                         trial_curr.df$density_traj_type,
                         trial_curr.df$target_density_traj_type,
                         trial_curr.df$trial_id,
                         trial_curr.df$target_set)
  
  log_msg(sprintf("[%s] Starting", trial_label))
  
  target_set_curr <- as.numeric(strsplit(trial_curr.df$target_set, split = "-")[[1]])
  trial_type <- sprintf("%s-%s", 
                        trial_curr.df$density_traj_type, 
                        trial_curr.df$target_density_traj_type)
  
  trial_curr_frames.df <- density_per_frame_tables_all.df %>% 
    filter(trial_num == trial_curr.df$trial_num, 
           i_dataset == trial_curr.df$i_dataset) 
  
  circleFun <- function(center = c(0,0), diameter = 1, npoints = 100){
    r = diameter / 2
    tt <- seq(0, 2*pi, length.out = npoints)
    xx <- center[1] + r * cos(tt)
    yy <- center[2] + r * sin(tt)
    return(data.frame(x = xx, y = yy))
  }
  dat_circle <- circleFun(c(0,0), 20, npoints = 200)
  
  p <- ggplot() +
    geom_path(data = dat_circle, aes(x, y)) + 
    geom_point(data = trial_curr_frames.df, 
               aes(x = x_coord, y_coord, colour = circle_color),
               size = 5, show.legend = FALSE) +
    scale_colour_manual(values = c("blue" = "blue", "violet" = "violet", "yellow" = "yellow")) + 
    coord_fixed() +
    theme_void() + 
    ggtitle("Frame: {frame_time}")
  
  anim <- p + transition_time(frame_num) +
    ease_aes("linear")
  
  anim_save(filename = sprintf("trial_%s_%s_%s.mp4", trial_type, trial_curr.df$trial_id, trial_curr.df$target_set), 
            animation = anim, 
            path = video_dir,
            nframes = 361, fps = 60, 
            width = 600, height = 600, 
            renderer = av_renderer())
  
  log_msg(sprintf("[%s] Done", trial_label))
}


# ─────────────────────────────────────────────
# 2. Parallel wrapper
# ─────────────────────────────────────────────

save_videos_parallel <- function(potential_trials.df, density_per_frame_tables_all.df,
                                 video_dir = "Videos/",
                                 log_dir   = "logs/videos/",
                                 n_cores   = 5) {
  
  dir.create(video_dir, showWarnings = FALSE, recursive = TRUE)
  dir.create(log_dir,   showWarnings = FALSE, recursive = TRUE)
  
  # Failsafe: derive the expected filename for each trial, skip already saved videos
  potential_trials.df <- potential_trials.df %>%
    mutate(video_filename = sprintf("trial_%s-%s_%s_%s.mp4",
                                    density_traj_type,
                                    target_density_traj_type,
                                    trial_id,
                                    target_set),
           video_path = file.path(video_dir, video_filename))
  
  trials_todo.df <- potential_trials.df %>%
    filter(!file.exists(video_path))
  
  n_done <- nrow(potential_trials.df) - nrow(trials_todo.df)
  message(sprintf("%d / %d videos already saved. %d remaining.",
                  n_done, nrow(potential_trials.df), nrow(trials_todo.df)))
  
  if (nrow(trials_todo.df) == 0) {
    message("Nothing to do — all videos already exist.")
    return(invisible(NULL))
  }
  
  # Split the todo dataframe into a list of single-row dataframes for parLapply
  trials_todo.list <- split(trials_todo.df, seq_len(nrow(trials_todo.df)))
  
  cl <- makeCluster(n_cores)
  
  tryCatch({
    clusterExport(cl, varlist = c("save_video", "density_per_frame_tables_all.df",
                                  "video_dir", "log_dir", "probing_n_frames"),
                  envir = environment())
    clusterEvalQ(cl, {
      library(dplyr)
      library(ggplot2)
      library(gganimate)
      library(av)
      # Assign each worker a dedicated log file named by its PID
      worker_log_file <<- file.path(log_dir, sprintf("worker_%d.log", Sys.getpid()))
    })
    
    parLapply(cl, trials_todo.list, function(trial_curr.df) {
      save_video(trial_curr.df            = trial_curr.df,
                 density_per_frame_tables_all.df = density_per_frame_tables_all.df,
                 video_dir               = video_dir,
                 log_file                = worker_log_file)
    })
    
  }, finally = {
    stopCluster(cl)
  })
  
  # Write completion summary to main log
  cat(sprintf("%s | All videos complete.\n", format(Sys.time(), "%Y-%m-%d %H:%M:%S")),
      file = file.path(log_dir, "main.log"), append = TRUE)
  
  message("Done. All videos saved to: ", video_dir)
  return(invisible(NULL))
}

```

```{r save-videos-density-throughout}
#| echo: false
#| include: false

# As participants will see them
circles_with_all_tracking_frames_threshold_density.df <- 
  readRDS(file = "Tables/circles_with_all_tracking_frames_threshold_density.rds")
info_per_frame_traj_density_throughout.df <- 
  readRDS(file = "Tables/info_per_frame_traj_density_throughout.rds") %>% 
    mutate(circle_type = ifelse(circle_num %in% target_set_curr, 
                                "target", "distractor"), 
           circle_color = ifelse(circle_type == "target" & 
                            frame_num <= probing_n_frames, 
                          "blue", "yellow")) %>% 
    select(!circle_id)

save_videos_parallel(
  potential_trials.df             = circles_with_all_tracking_frames_threshold_density.df,
  density_per_frame_tables_all.df = info_per_frame_traj_density_throughout.df,
  video_dir                       = "Videos/",
  log_dir                         = "logs/videos/",
  n_cores                         = 5)

# With target marked
circles_with_all_tracking_frames_threshold_density.df <- 
  readRDS(file = "Tables/circles_with_all_tracking_frames_threshold_density.rds")
info_per_frame_traj_density_throughout_highlighted.df <- 
  readRDS(file = "Tables/info_per_frame_traj_density_throughout.rds") %>% 
    mutate(circle_type = ifelse(circle_num %in% target_set_curr, 
                                "target", "distractor"), 
           circle_color = case_when(
             circle_type == "target" & frame_num <= probing_n_frames ~ "blue", 
             circle_type == "target" & frame_num > probing_n_frames ~ "violet",
            .default = "yellow")) %>% 
    select(!circle_id)

save_videos_parallel(
  potential_trials.df             = circles_with_all_tracking_frames_threshold_density.df,
  density_per_frame_tables_all.df = info_per_frame_traj_density_throughout_highlighted.df,
  video_dir                       = "Videos_With_Targets_Highlighted/",
  log_dir                         = "logs/videos/",
  n_cores                         = 5)

```

```{r save-videos-density-throughout}
#| echo: false
#| include: false


circles_high_low_threshold_density.df <- 
  readRDS(file = "Tables/circles_high_low_threshold_density.rds")
info_per_frame_low_to_high_and_high_to_low.df <- 
  readRDS(file = "Tables/info_per_frame_low_to_high_and_high_to_low.rds")  %>% 
    mutate(circle_type = ifelse(circle_num %in% target_set_curr, 
                                "target", "distractor"), 
           circle_color = ifelse(circle_type == "target" & 
                            frame_num <= probing_n_frames, 
                          "blue", "yellow")) %>% 
    select(!circle_id)

save_videos_parallel(
  potential_trials.df             = circles_high_low_threshold_density.df,
  density_per_frame_tables_all.df = info_per_frame_low_to_high_and_high_to_low.df,
  video_dir                       = "Videos/",
  log_dir                         = "logs/videos/",
  n_cores                         = 5)


# With target marked
circles_high_low_threshold_density.df <- 
  readRDS(file = "Tables/circles_high_low_threshold_density.rds")
info_per_frame_low_to_high_and_high_to_low.df <- 
  readRDS(file = "Tables/info_per_frame_low_to_high_and_high_to_low.rds") %>% 
    mutate(circle_type = ifelse(circle_num %in% target_set_curr, 
                                "target", "distractor"), 
           circle_color = case_when(
             circle_type == "target" & frame_num <= probing_n_frames ~ "blue", 
             circle_type == "target" & frame_num > probing_n_frames ~ "violet",
            .default = "yellow")) %>% 
    select(!circle_id)

save_videos_parallel(
  potential_trials.df             = circles_high_low_threshold_density.df,
  density_per_frame_tables_all.df = info_per_frame_low_to_high_and_high_to_low.df,
  video_dir                       = "Videos_With_Targets_Highlighted/",
  log_dir                         = "logs/videos/",
  n_cores                         = 5)

```


# Target Density Low/High Throughout

Here we look for sets of five (5) circles with density within themselves that is below/above the threshold throughout the tracking period. This is done using the scripts:

1. `MOT_Sequence_Target_Density_Parallel_Claude3.qmd` to compute the density within each possible set of five (5) circles for the potential trials identified above with five (5) circles that have low/high density throughout the tracking period, 
2. `MOT_Sequence_Target_Density_Analysis.qmd` to identify and make a video of all the potential target sets that have been identified to have a density between themselves above/below the threshold throughout the tracking period within the trials identified above.

The goal now is to identify sets of trials and targets sets such that : 
- among the trials with targets that have `low overall density`, find target sets with `high target density`, 
- among the trials with targets that have `high overall density`, find target sets with `low target density`,





