---
title: "MOT_Sequence_Target_Density_Analysis"
author: "Freya Joessel"
editor: source
date: today
toc: true
toc-depth: 5
# toc-expand: true
number-sections: true
highlight-style: pygments
toc-location: left
reference-location: margin
citation-location: margin
format:
  html: 
    code-fold: true
    html-math-method: katex
---

Use this script after the script "MOT_Sequence_Target_Density_Parallel_Claude_3.qmd" has been run

```{r preamble}
#| echo: false
#| include: false

library(dplyr)
library(progress)
library(ggplot2)
library(purrr)
library(gganimate)
# detach("package:gganimate", unload = T)

```

```{r load-data}
#| echo: false
#| cache: true
#| include: false

data_dir_below <- "Tables/Target_Densities/Sequences_Below"
data_dir_above <- "Tables/Target_Densities/Sequences_Above"

files_list_below <- list.files(path = data_dir_below, pattern = "*.rds", full.names = T)
files_list_above <- list.files(path = data_dir_above, pattern = "*.rds", full.names = T)
```

```{r task-parameters}
#| echo: false
#| include: false

n_targets_in_experiment <- 5

tracking_duration_s <- 4
trial_duration_s <- 6
probing_duration <- trial_duration_s - tracking_duration_s
trial_n_frames <- 361
probing_n_frames <- probing_duration*(trial_n_frames - 1)/trial_duration_s + 1
tracking_n_frames <- trial_n_frames - probing_n_frames

```

# Threshold for target density

The threshold for target density will be the median across all possible combinations of 5 targets of the mean target density across all frames and circles in the trials we analyzed. 

```{r compute-mean-target-density-per-trial}
#| echo: false
#| cache: true
#| include: false

if(file.exists(file.path("Tables", "target_densities_means_above.rds"))) {
    target_density.df <- readRDS(file = file.path("Tables", "target_densities_means_above.rds"))
} else {
  target_density_threshold <- list()
  
  n_files <- length(files_list)
  pb <- progress_bar$new(format = "(:spin) [:bar] eta :eta", total = n_files)
  pb$tick(0)
  
  for (i_file in seq_along(files_list)) {
    target_densities_curr.df <- readRDS(files_list[[i_file]])
    
    target_density_threshold[[i_file]] <- target_densities_curr.df %>% 
      select(target_set, target_density) %>% 
      group_by(target_set) %>% 
      summarize(target_density_mean = mean(target_density/4))
    
    pb$tick(1)
  }
    
  target_density.df <- bind_rows(target_density_threshold)
  
  write.csv(x = target_density.df, file = file.path("Tables", "target_densities_means_above.csv"))
  saveRDS(object = target_density.df, file = file.path("Tables", "target_densities_means_above.rds"))
}

```


```{r compute-target-density-threshold}
#| echo: false
#| cache: false
#| include: false

target_density_threshold <- median(target_density.df$target_density_mean)/4

```

```{r n-frames-under-threshold-per-target-sets-and-trials-tracking-period} 
#| echo: false
#| include: false

if(file.exists(file.path("Tables", "target_density_n_frames_below_above.rds"))) {
  target_density_n_frames_below_above.df <- readRDS(file = file.path("Tables", "target_density_n_frames_below_above.rds"))
} else {
  n_files <- length(files_list_above)
  pb <- progress_bar$new(format = "(:spin) [:bar] eta :eta", total = n_files)
  pb$tick(0)
  
  target_density_n_frames_below <- list()
  
  for (i_file in seq_along(files_list_above)) {
    target_densities_curr.df <- readRDS(files_list_above[[i_file]])
    
    target_density_n_frames_below[[i_file]] <- target_densities_curr.df %>% 
      filter(frame_num > probing_n_frames) %>%
      mutate(target_density = target_density/4) %>% 
      group_by(target_set, circle_num, i_dataset, trial_num, trial_id) %>% 
      dplyr::summarize(n_frames_below = sum(target_density < target_density_threshold), .groups = "keep")
    
    pb$tick(1)
  }
  
  target_density_n_frames_below.df <- bind_rows(target_density_n_frames_below)

  write.csv(x = target_density_n_frames_below.df, 
            file = file.path("Tables", "target_density_n_frames_below_above.csv"))
  saveRDS(object = target_density_n_frames_below.df, 
          file = file.path("Tables", "target_density_n_frames_below_above.rds"))  
}


if(file.exists(file.path("Tables", "target_density_n_frames_below_below.rds"))) {
  target_density_n_frames_below_below.df <- readRDS(file = file.path("Tables", "target_density_n_frames_below_below.rds"))
} else {
  n_files <- length(files_list_below)
  pb <- progress_bar$new(format = "(:spin) [:bar] eta :eta", total = n_files)
  pb$tick(0)
  
  target_density_n_frames_below <- list()
  
  for (i_file in seq_along(files_list_below)) {
    target_densities_curr.df <- readRDS(files_list_below[[i_file]])
    
    target_density_n_frames_below[[i_file]] <- target_densities_curr.df %>% 
      filter(frame_num > probing_n_frames) %>%
      mutate(target_density = target_density/4) %>% 
      group_by(target_set, circle_num, i_dataset, trial_num, trial_id) %>% 
      dplyr::summarize(n_frames_below = sum(target_density < target_density_threshold), .groups = "keep")
    
    pb$tick(1)
  }
  
  target_density_n_frames_below.df <- bind_rows(target_density_n_frames_below)

  write.csv(x = target_density_n_frames_below.df, 
            file = file.path("Tables", "target_density_n_frames_below_below.csv"))
  saveRDS(object = target_density_n_frames_below.df, 
          file = file.path("Tables", "target_density_n_frames_below_below.rds"))  
}


```

```{r find-trials-and-target-sets-with-target-density-above-below-threshold} 
#| echo: false
#| include: false

target_density_n_frames_below_below_count.df <- target_density_n_frames_below_below.df %>% 
  group_by(target_set, i_dataset, trial_num, trial_id) %>% 
  summarize(n_circles_all_frames_below = sum(n_frames_below == 240), 
            n_circles_all_frames_above = sum(n_frames_below == 0), 
            .groups = "drop")

target_density_below_below_below_potential_trials.df <- target_density_n_frames_below_below_count.df %>% 
  filter(n_circles_all_frames_below == 5) %>%
  select(i_dataset, trial_num, trial_id, target_set, n_circles_all_frames_below) %>% 
  arrange(i_dataset, trial_num, target_set)

target_density_below_below_above_potential_trials.df <- target_density_n_frames_below_below_count.df %>% 
  filter(n_circles_all_frames_above == 5) %>%
  select(i_dataset, trial_num, trial_id, target_set, n_circles_all_frames_above) %>% 
  arrange(i_dataset, trial_num, target_set)


```

# Show an example 

## Density : Below / Target Density : Below 

```{r load-data}
#| echo: false
#| cache: true
#| include: false

density_per_frame_tables_all.df <- readRDS(file = "Tables/density_per_frame_tables_all.rds")

```


```{r find-trials-and-target-sets-with-target-density-above-below-threshold} 
#| echo: false
#| include: false


video_dir <- "Videos"

potential_trial_idx <- 1 
trial_type <- "below_below"
  
  
trial_curr.df <- 
  target_density_below_below_below_potential_trials.df[potential_trial_idx,]
target_set_curr <- as.numeric(strsplit(trial_curr.df$target_set, split = "-")[[1]])

trial_curr_frames.df <- density_per_frame_tables_all.df %>% 
  filter(trial_num == trial_curr.df$trial_num, 
         i_dataset == trial_curr.df$i_dataset) %>% 
  mutate(circle_type = ifelse(circle_num %in% target_set_curr, 
                              "target", "distractor"), 
         circle_color = ifelse(circle_type == "target" & 
                          frame_num <= probing_n_frames, 
                        "blue", "yellow")) %>% 
  select(!circle_id)

circleFun <- function(center = c(0,0),diameter = 1, npoints = 100){
    r = diameter / 2
    tt <- seq(0,2*pi,length.out = npoints)
    xx <- center[1] + r * cos(tt)
    yy <- center[2] + r * sin(tt)
    return(data.frame(x = xx, y = yy))
}
dat_circle <- circleFun(c(0,0),20,npoints = 200)

p <- ggplot() +
  # geom_circle(aes(x0 = 0, y0 = 0, r = 10), fill = "grey", color = "black") +
  geom_path(data = dat_circle, aes(x,y)) + 
  geom_point(data = trial_curr_frames.df, 
            aes(x = x_coord, y_coord, colour = circle_color),
            size = 5, show.legend = FALSE) +
  scale_colour_manual(values = c("blue", "yellow")) + 
  coord_fixed() + # Ensures the circle isn't oval
  theme_void()

anim <- p + transition_time(frame_num) +
  ease_aes("linear")

anim_save(filename = sprintf("trial_%s_%s_%s.mp4", trial_type, trial_curr.df$trial_id, trial_curr.df$target_set), 
          animation = anim, 
          path = video_dir,
          nframes = 361, fps = 60, 
          width = 600, height = 600, 
          renderer = av_renderer())

```

## Density : Below / Target Density : Above 


